Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-20 paper.tex
conclusions

\section{\uppercase{Working with AWS}}
\label{sec:aws}
In this section, first of all, the current user-level features 
provided by the Amazon Web Services are explained and analyzed 
from the point of view of the GPU usage. 
Finally, the scenarios and experiments where virtualized GPUs are utilized are 
described and first results are showed.

@@

\section{\uppercase{Conclusions}}
\label{sec:conclusions}
We have presented an upgrade for Openstack which easily permits to create GPU-instances and manage the physical GPUs to make more profit of them.

@@

\section*{\uppercase{Acknowledgements}}
The authors would like to thank the IT members of the department Vicente Roca and Gustavo Edo for their help.

>>>>

\section{\uppercase{Working with AWS}}
\label{sec:workingaws}
In this section, first of all, the current user-level features 
provided by the Amazon Web Services are explained and analyzed 
from the point of view of the GPU usage. 
Finally, the scenarios and experiments where virtualized GPUs are utilized are 
described and first results are showed.

@@

\section{\uppercase{Conclusions}}
\label{sec:conclusions}
We have seen a thoroughly study of the possibilities offered by AWS in everything to do with GPUs. Its limitations drove us to deploy our own private cloud to have more flexibility when working with these accelerators.
So that, we have presented an upgrade for Openstack which easily permits to create GPU-instances and manage the physical GPUs to make more profit of them.

Leaving aside the performance of the executions which we knew in advance that would be poor due to the interconnection network features, we have created new operation modes. They have brought interesting new ways of using GPUs in situations where the simple fact of having accessing a GPU is more important than having a powerful GPU to boost the performance.

@@

\section*{\uppercase{Acknowledgements}}
The authors would like to thank the IT members of the department Gustavo Edo and Vicente Roca for their help.
